### 2019-04-13 paper/paper.tex
small typo fixes

We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}, and then %TODO fix this footnote, underscores are cursed
downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the npm registry skimdb
, which we then converted to a somewhat simplified form as in Listing \ref{sampleSimpleMetadata} with just version and dependency information as this is all
we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and $devDependencies$ used in testing and development.\\

We gathered some information on download counts for \code{npm} packages from the npmjs API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
however we found that the npmjs API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
historic download counts for \code{npm} as a whole or any specific packages.\\

@@

As in the original paper we analyzed popularity of \code{npm} packages using three major measures
\begin{enumerate}
  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
    package metadata as described in Section \ref{Package Metadata}. PageRank is calculated for every package using a damping factor of 0.85 
    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
    \code{npm} rank, an relative ranking of packge popularity with 1 being the most popular.
  \item \textbf{download rank}
\end{enumerate}

>>>>

We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}, and then %TODO fix this footnote, underscores are cursed
downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the \code{npm} registry skimdb
, which we then converted to a somewhat simplified form as in Listing \ref{sampleSimpleMetadata} with just version and dependency information as this is all
we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and \code{devDependencies} used in testing and development.\\

We gathered some information on download counts for \code{npm} packages from the \code{npm} API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
however we found that the npmjs API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
historic download counts for \code{npm} as a whole or any specific packages.\\

@@

As in the original paper we analyzed popularity of \code{npm} packages using three major measures
\begin{enumerate}
  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
    package metadata as described in Section \ref{Package Metadata}. PageRank is calculated for every package using a damping factor of 0.85 
    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
  \item \textbf{download rank}
\end{enumerate}
